Weather Data Integration and Assimilation System\\

### 2020-02-11 Paper.tex
After 2nd review

@@

\author{\IEEEauthorblockN{Gihan Karunarathne}
\IEEEauthorblockA{\textit{dept. computer science and Engineering} \\
\textit{university of moratuwa}\\
Moratuwa, Sri Lanka \\
gihan.09@cse.mrt.ac.lk}
\and
\IEEEauthorblockN{Dr. Dilum Bandara}
\IEEEauthorblockA{\textit{dept. computer science and Engineering} \\
\textit{university of moratuwa}\\
Moratuwa, Sri Lanka \\
dilumb@cse.mrt.ac.lk}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}. It uses the modern architecture pattern such as microservice in order to achieve the scalability, rather using monolithic architecture or client service architecture. It provides a modular approach to integration data from different sources and export into different formats. Also the inbuilt extension module system allow users to add new features. The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs. The paper describes the initial design goals, evolve over few architectures to get desired performance, and explains how the system in way to achieve scalability. Later we analyse the performance test observations with the performance metrics.
\end{abstract}

\begin{IEEEkeywords}
\acrshort{wdias}, weather, microservice, kubernetes, hierarchical database 
\end{IEEEkeywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
I'm going to do this today \cite{Haggett1998AnWales}.
Give general idea on weather data integration systems.
Talk about the existing systems. And they're proprietary or close source.
(Don't dedicate another section, otherwise need to do a comparison at the performance analysis)
At the end the structure of rest of the paper

@@

TODO: Specify the \acrshort{lead} service as a building block approach. \acrshort{fews} more modular approach with general adapter. And \acrshort{wdias} using microservice as module.
Similar to the \acrfull{fews} \cite{WERNER2004DELFT-FEWS:SYSTEM}

@@

TODO: Update content as below, overview of rest of the paper
This paper first provides a short review of the operational forecasting process and the role of Delft-FEWS within that process. Section 3 provides an overview of the philosophy and the most important components and features of Delft-FEWS, while Section 4 discusses some example applications of the Delft-FEWS system in research and operations. A discussion of the systems strengths and limitations is provided in Section 5. Section 6 finally provides a summary of the paper, as well as an outlook on the future development of Delft-FEWS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Modules of Weather Data System}
The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Components of a weather data system.}
\label{fi:wdia_components}
\end{figure}
\paragraph{Integration} The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\paragraph{Assimilation} Then the system should be able to fulfill weather models varying data requirements. Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
\paragraph{Dissemination} Then different users should be able to retrieve data as they required. Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Structure of \acrshort{wdias}}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}}
\caption{microservice architecture - handle on demand.}
\label{fi:microservice_architecture_on_demand}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance Analysis}

\subsection{Test Plan and Workload}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
\caption{Performance study.}
\label{fi:performance_Study}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Strengths and Limitations}
\paragraph{Lack of data preprossessing modules}
The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals. Also \acrshort{wdias} provide a more generic open interface approach to create more preprocessing modules. Since \acrshort{wdias} is an open source system, it expect more modules to be create by the community. When compared to other system like \acrshort{fews}, current system only have few extension for the testing purpose. This is one of the major area that need to be improved.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}. Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.
We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}. It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data. And compatible with current cloud computing technologies and architecture patterns.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

>>>>

\usepackage{todonotes}
\newcommand{\db}[1]{\textcolor{blue!40}{#1}}
\newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}

@@

\author{\IEEEauthorblockN{Gihan Karunarathne}
\IEEEauthorblockA{\textit{Dept. Computer Science and Engineering} \\
\textit{University of Moratuwa}\\
Katubedda, Sri Lanka \\
gihan.09@cse.mrt.ac.lk}
\and
\IEEEauthorblockN{H.M.N. Dilum Bandara}
\IEEEauthorblockA{\textit{Dept. Computer Science and Engineering} \\
\textit{University of Moratuwa}\\
Katubedda, Sri Lanka \\
dilumb@cse.mrt.ac.lk}
\and
\IEEEauthorblockN{Srikantha Herath}
\IEEEauthorblockA{\textit{Center for Urban Water, Sri Lanka} \\
%\textit{Center for Urban Water, Sri Lanka}\\
Battaramulla, Sri Lanka \\
admin@curwsl.org}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}. It uses the modern architecture pattern such as microservice in order to achieve the scalability, rather using monolithic architecture or client service architecture. It provides a modular approach to integration data from different sources and export into different formats. Also the inbuilt extension module system allow users to add new features. The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs. The paper describes the initial design goals, evolve over few architectures to get desired performance, and explains how the system in way to achieve scalability. Later we analyse the performance test observations with the performance metrics.

\db{Numerical Weather Models (NWMs) utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to using such multimodal data into a NWM, it is necessary to transcode data into a format that can be ingested by the NWM. Moreover, the data integration system’s response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of NWMs. The resulting weather data also need to be accessed by many researchers and third-party applications. Even though there are several weather data integration systems, they are based on monolithic or client-server architectures and are unable to benefit from novel computational models such as cloud computing and containers. Moreover, most of this software is proprietary or closed sourced; hence, it is difficult to customize such software for an island like Sri Lanka with different weather seasons. Therefore, in this research, we propose Weather Data Integration and Assimilation System (WDIAS) that utilizes modern architecture pattern such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. WDIAS provides a modular architecture to integrate data from different sources, export into different formats, and the inbuilt extension module system allow users to add new features. We demonstrate the utility of WDIAS using cloud-based experimental setup and weather-related synthetic workloads.}
\end{abstract}

\begin{IEEEkeywords}
\db{Data assimilation, data integration, hierarchical databases, microservice, weather}
\end{IEEEkeywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%I'm going to do this today \cite{Haggett1998AnWales}.
Give general idea on weather data integration systems.
Talk about the existing systems. And they're proprietary or close source.
(Don't dedicate another section, otherwise need to do a comparison at the performance analysis)
At the end the structure of rest of the paper

@@

TODO: Specify the \acrshort{lead} service as a building block approach. \acrshort{fews} more modular approach with general adapter. And \acrshort{wdias} using microservice as module.
Similar to the \acrfull{fews} \cite{Werner2013TheSystem}

@@

TODO: Update content as below, overview of rest of the paper
This paper first provides a short review of the operational forecasting process and the role of Delft-FEWS within that process. Section 3 provides an overview of the philosophy and the most important components and features of Delft-FEWS, while Section 4 discusses some example applications of the Delft-FEWS system in research and operations. A discussion of the systems strengths and limitations is provided in Section 5. Section 6 finally provides a summary of the paper, as well as an outlook on the future development of Delft-FEWS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\db{Background}}
%\section{Modules of Weather Data System}
Fig. \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Components of a weather data system.}
\label{fi:wdia_components}
\end{figure}
\paragraph{Integration} The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\paragraph{Assimilation} Then the system should be able to fulfill weather models varying data requirements. Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
\paragraph{Dissemination} Then different users should be able to retrieve data as they required. Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\acrfull{wdias} Architecture}
%\section{Structure of \acrshort{wdias}}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}}
\caption{microservice architecture - handle on demand.}
\label{fi:microservice_architecture_on_demand}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance \db{Evaluation}}
%\section{Performance Analysis}
\subsection{Test Plan and Workload}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
\caption{Performance study.}
\label{fi:performance_Study}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Strengths and Limitations}
\dbc{Make this the dicussion and a sub-section of Sec. 4}

\paragraph{Lack of data preprossessing modules}
The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals. Also \acrshort{wdias} provide a more generic open interface approach to create more preprocessing modules. Since \acrshort{wdias} is an open source system, it expect more modules to be create by the community. When compared to other system like \acrshort{fews}, current system only have few extension for the testing purpose. This is one of the major area that need to be improved.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\dbc{Summary is too long. Should not be more than a single para}
To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}. Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.
We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}. It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data. And compatible with current cloud computing technologies and architecture patterns.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgment}
\db{This research is supported in part by the grant from the Center for Urban Water, Sri Lanka.}

### 2020-02-11 introduction/sec_1-motivation.tex
After 2nd review

Weather prediction can use to reduce the lost in natural disasters and in order to gain more advantage over the natural resources like water management. The weather predictions are performed via \acrfull{nwm} by providing different configurations and the current status of the environment such as temperature, rainfall, and wind direction etc. For weather prediction \acrfull{wrf} model is used for predicting the rain fall, temperature, and wind direction etc. Then using the real time observations, the correct model is selected and after removing the bias, extract the information and feed into the next models. There are lots of \acrshort{nwm} available there, but another example can be taken as FLO2D which can be used to predict the water level on the ground. For the corresponding model developed based on the geo data, giving the current status of water levels and forecasted rainfall, the model predict the forecasted water level.

CUrW SL is a government ministry which is working on weather data forecasting for Sri Lanka in order to reduce the natural disaster effects in Sri Lanka. In order to do that, it is implementing its own system with the idea of long term maintainability rather depend on existing vendors. It collected real time weather data from weather stations and other government entities, and do the forecasting daily. Then the generated results are shared to the trusted parties. One of the future goals of CUrW SL to open up to the public to share the data, and use of the processed data via their system for the betterment of the society. The institute is operating via the paid TAX of Sri Lankan, and its trying to improve the quality of the life and the economic lost which are effected on the country via sharing the data for external parties to use of them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}. These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

@@

>>>>

Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water. The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input. For example, the \acrfull{wrf} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the correct model is selected. After removing the bias, the extract information is then fed into the next set of models. \db{There are lots of \acrshort{nwm} available there, but another example can be taken as FLO2D which can be used to predict the water level on the ground. For the corresponding model developed based on the geo data, giving the current status of water levels and forecasted rainfall, the model predicts the forecasted water level.}
\dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
\dbc{cite both NWM and WRF}

Center for Urban Water, Sri Lanka (CUrW-SL) is tasked with the mission to reduce water-related natural disasters in Sri Lanka. CURW-SL is implementing its own system with the idea of long-term maintainability rather depend on existing weather data integration systems. It collected real-time data from weather stations and other government entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management. One of the future goals of CUrW-SL is to open up data to the public enabling both societal and commercial use cases. % and , and use of the processed data via their system for the betterment of the society. The institute is operating via the paid TAX of Sri Lankan, and its trying to improve the quality of the life and the economic lost which are effected on the country via sharing the data for external parties to use of them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

@@

\dbc{Citations need to be given for DIAS, WDIA, FEWS, FLOW2D, etc. By the way, don't remove my comments (you are welcome to comment on them). I need them to check whether those are addressed. When I see them addressed, I'll remove comments.}

### 2020-02-11 introduction/sec_2-problem_and_objectives.tex
After 2nd review

\section{Problem Statement}
Handling spatio-temporal weather data is challenging. Need an extendable system to support weather models by efficiently storing and retrieving data. Therefore, in this context the problem can be state as;
\emph{necessaty of a Data Integration System which is scalable, highly available and capable of 
interact with different data formats including spatio-temporal bulk stream data, 
store efficiently while optimizing the disk space,
support geographical and time-base queries,
third parties can access the data with easy integration, and
able to easy modify and use based on the requirements.
}

\section{Objectives}
We address above problem statement by achieving the following objectives:
\begin{itemize}
    \item To develop an open platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize schema to support data queries based on geography and time
    \item To develop an API to share data
    \item To use open source tools and provide the source publicly with appropriate liecense.
\end{itemize}

>>>>

\section{Problem Statement}
Handling spatio-temporal weather data is challenging \db{as ...}. Moreover, the data integration system needs to be capable of interacting with different data formats including spatio-temporal bulk stream data. Furthermore, it should support geographical and time-base queries, as well as provide third-party access to data with easy integration. Scalability and high availability are also essential to support different use cases and mission-critical nature of applications. Therefore, we need an extendable system to support weather models by efficiently ingesting, storing, and retrieving data. In this context, the research problem can be stated as follows:

\emph{....}
\dbc{Give a proper problem statement.}

\section{Objectives}
We address above problem statement by achieving the following research objectives:
\begin{itemize}
    \item To develop an open platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize schema to support data queries based on geography and time
    \item To develop an API for third-party data sharing
%    \item To use open source tools and provide the source publicly with appropriate liecense.
\end{itemize}

### 2020-02-11 introduction/sec_3-outline.tex
conc to summary
Misc fixes on references
After 2nd review

\section{Outline}
The rest of the thesis is organized as follows. Literature review is presented in Chapter \ref{ch:literature}. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. Performance analysis is presented in Chapter \ref{ch:results} while summary and future work are presented in Chapter \ref{ch:conc}.
\dbc{Expand a bit by adding at least 1 more sentence for each chapter.}

>>>>

\section{Outline}
The rest of the thesis is organized as follows. Literature review is presented in Chapter \ref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. It provides details about how the \acrshort{wdias} is design by following a microservice architecture and the date preprocessing capabilities of the system. Performance analysis is presented in Chapter \ref{ch:results}. Here we discuss experiment setup of the \acrshort{wdias} and analyze the observations with respect to performance metrics. Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed about the research limitations and future work.
